The Astropy Project

### 2017-11-10 main.tex
clean up dev model section

\subsection{APEs - Astropy Proposals for Enhancement}
%draft by hamogu
%edited by Adrian PW

@@

\subsection{Astropy development model}
\inlinecomment{Adrian started this, but needs some filling in by EJT}

@@

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This line count includes comments, as these are often as important for maintainability as the code itself.  Without comments there are $142197$ lines of code} contributed by $232$ unique
contributors over $19270$ \texttt{git} commits.
The commit distribution follows an approximate power-law (with log-slope of $\sim -0.47$), meaning most of the commits were and are contributed by a relatively small fraction of the contributor pool. $\sim 50$ percent of the commits were contributed by the top $4$ contributors, while $\sim 90$ percent of the commits came from the top $24$.

>>>>

\subsection{APEs - Astropy Proposals for Enhancement}
% draft by hamogu
% edited by Adrian PW

@@

\subsection{Astropy development model}
% draft by Adrian PW and Erik T.

@@

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits.
The commit distribution follows an approximate power-law (with log-slope of
$\sim -0.47$), meaning most of the commits were and are contributed by a
relatively small fraction of the contributor pool.
$\approx 50$ percent of the commits were contributed by the top $4$
contributors, while $\sim 90$ percent of the commits came from the top $24$
contributors.
